---
title: RCoinAPI - Part 2
author: Ramshreyas Rao
date: '2021-07-15'
slug: []
categories:
  - Crypto
tags: []
lastmod: '2021-07-15T12:18:15+05:30'
keywords: []
description: ''
comment: no
toc: no
autoCollapseToc: no
postMetaInFooter: no
hiddenFromHomePage: no
contentCopyright: no
reward: no
mathjax: no
mathjaxEnableSingleDollar: no
mathjaxEnableAutoNumber: no
hideHeaderAndFooter: no
flowchartDiagrams:
  enable: no
  options: ''
sequenceDiagrams:
  enable: no
  options: ''
---

# A closer look

![](images/Closer_Look_(5711020957).jpg)

In [Part 1](http://localhost:4321/post/2021-07-05-rcoinapi/), we used RCoinAPI to get ETH/USD data to create and backtest a very simple Golden/Death-cross strategy. In part deux, let's take a closer look at the OHLCV methods exposed by RCoinAPI. We will quickly get a sense of what is on offer, and how well it plays with familiar [quantmod](https://cran.r-project.org/web/packages/quantmod/quantmod.pdf) commands.

## Setup

Load the library

``` {r, warning=FALSE, message=FALSE}
library(rcoinapi)
library(quantmod)
```

Set your API key (Get your API key at
<https://www.coinapi.io/pricing?apikey>)

``` r
setApiKey("XXXXXXXXXXXXXXX")
```

## OHLCV

To make OHLCV requests, we first need to set the periodicity of the returned xts object. Unlike [quantmod](https://cran.r-project.org/web/packages/quantmod/quantmod.pdf), where the [getSymbols](https://www.rdocumentation.org/packages/quantmod/versions/0.4.18/topics/getSymbols) function always returns data with a 1-day perdiodicity, we need to specify the candle duration. 

So to get valid periodIds for OHLCV requests:

``` {r}
getOHLCVPeriods()
```

Self-explanatory, I trust.

We will now use one of these periodIds to request data for a given 'symbol'. In CoinAPI nomenclature, symbols refer to specific instruments on exchanges, like the BTC/USD spot market pair on Bitstamp,  BITSTAMP_SPOT_BTC_USD. 'Assets' refer to the underlying asset, like BTC, or USD.

To list all symbols available in CoinAPI, just run one of:

```r
getCryptoSymbols()
getCryptoSymbols(filterSymbolId = "BTC")
getCryptoSymbols(filterSymbolId = "BTC", filterAssetId = "USD")
getCryptoSymbols(filterSymbolId = "BTC", filterAssetId = "USD", exchangeId = "FTX")
```

To get the 25 latest data for BITSTAMP_SPOT_BTC_USD:

``` {r}
getLatestOHLCV("BITSTAMP_SPOT_BTC_USD", periodId = "1MIN", limit = 25)
head(BITSTAMP_SPOT_BTC_USD)
```
As you can see, this returns an xts object much like that returned by quantmod's [getSymbols](https://www.rdocumentation.org/packages/quantmod/versions/0.4.18/topics/getSymbols). So we can:

```{r}
head(Hi(BITSTAMP_SPOT_BTC_USD))
```

Confirm the periodicity:
```{r}
periodicity(BITSTAMP_SPOT_BTC_USD)
```

and [chartSeries](https://www.rdocumentation.org/packages/quantmod/versions/0.4.18/topics/chartSeries) quite handily:
```{r}
chartSeries(BITSTAMP_SPOT_BTC_USD)
```

We can also do this with assets (base and quote) to get aggregated results across multiple exchanges - ["If asset pairs are used then timeseries in the response will contain data consolidated across all most legitimate SPOT markets which contain both assets in any order."](https://docs.coinapi.io/#latest-data-get)
```{r}
getLatestOHLCV("BTC", "USD", periodId = "1HRS", limit = 25)
head(BTC_USD)
```
All of this data is 'latest' as defined by CoinAPI - for historical data of symbols:

``` {r}
getHistoricalOHLCV("BITSTAMP_SPOT_BTC_USD", periodId = "1MIN", timeStart = "2016-01-01T00:00:00", limit = 25)
head(BITSTAMP_SPOT_BTC_USD)
```
As you can see, this is now showing 2016 data for BITSTAMP_SPOT_BTC_USD.

For historical data of asset/base pairs aggregated across exchanges:
```{r}
getHistoricalOHLCV("BTC", "USD", periodId = "1MIN", timeStart = "2016-01-01T00:00:00", limit = 25)
head(BTC_USD)
```

And that's about it!

This winds up a quick whirlwind tour of how to get clean, OHLCV data in xts format using RCoinAPI, either from specific exchanges, or aggregated across exchanges. There is a lot more functionality, and full coverage of the CoinAPI functionality including Trades, Orderbooks, L3 and Quote data which the library covers - please see [https://github.com/Ramshreyas/rcoinapi](https://github.com/Ramshreyas/rcoinapi) for the full documentation.

