---
title: RCoinAPI - Part 1
author: Ramshreyas Rao
date: '2021-07-05'
slug: []
categories:
  - Crypto
tags: []
lastmod: '2021-07-05T17:22:53+05:30'
keywords: []
description: ''
comment: no
toc: no
autoCollapseToc: no
postMetaInFooter: no
hiddenFromHomePage: no
contentCopyright: no
reward: no
mathjax: no
mathjaxEnableSingleDollar: no
mathjaxEnableAutoNumber: no
hideHeaderAndFooter: no
flowchartDiagrams:
  enable: no
  options: ''
sequenceDiagrams:
  enable: no
  options: ''
---

# An R package for the CoinAPI.io REST API

This is the first in a series of posts detailing my first R package :smile:, providing access to CoinAPI.io's REST API. The goal of this package is to closely match the wonderful [Quantmod](https://cran.r-project.org/web/packages/quantmod/quantmod.pdf), so that you can add Crypto to your Quant workflow using CoinAPI data with as little pain as possible.

In this post, we'll use RCoinAPI to get Crypto data, create a trading strategy, and backtest it with [quantstrat](https://github.com/braverock/quantstrat). :sunglasses:

## Before you start

Documentation: https://github.com/Ramshreyas/rcoinapi

## Requirements

A working R ([RStudio, to make life easy](https://www.rstudio.com/products/rstudio/)) installation with [devtools](https://www.r-project.org/nosvn/pandoc/devtools.html) installed.

An API key: https://www.coinapi.io/pricing?apikey. The free one will do for our tutorial.

A basic understanding of [Crypto]()

A basic understanding of [indicators]()

Access to :coffee:

## Installation

<!-- You can install the released version of rcoinapi from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rcoinapi") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("Ramshreyas/rcoinapi")
```
## Setup

Load the library

``` {r}
library(rcoinapi)
```

Set your API key (Get your free API key at https://www.coinapi.io/pricing?apikey)

``` r
setApiKey("Replace with your API key")
```

Test if it's working by getting the list of exchanges that CoinAPI gives access to

``` r
getExchanges()
```

## THIS IS NOT FINANCIAL ADVICE

\'nuff said. :triumph:

## Your first crypto trading strategy

Any trading strategy helps you make only two decisions:

- When to buy
- When to sell

That's. It. If your strategy enables you to buy lower than you sell more often than not, you are making money (Ignoring some pesky but important funding issues that can bankrupt you before you make money etc... but we're not going to dwell on it). 

Probably the most commonly cited (and therefore the least likely to :full_moon:) demo strategy is the [Golden/Death cross](https://academy.binance.com/en/articles/golden-cross-and-death-cross-explained):

- BUY when the 50-day moving average crosses above the 200-day moving average
- SELL when the 50-day moving average crosses below the 200-day moving average

Of course, you could use weekly/monthly/minutely/whateverly MAs your little heart desires.

Let's backtest this trading strategy against historical data of BTC/USD using RCoinAPI and see how well it works.

### Step 1 - get historical prices of BTC. 

Let's get historical prices of ETH/USD, with a 1-Day periodicity, since 2016.

``` {r}
getHistoricalOHLCV("ETH", "USD", periodId = "1DAY", timeStart = "2016-01-01", limit = 1000)
```

Just like Quantmod, this creates a variable, BTC_USD, which contains the OHLCV data

``` {r}
head(ETH_USD)
```
Let's compare this with the [XTS](https://cran.r-project.org/web/packages/xts/xts.pdf) object returned by Quantmod:

``` {r, warning=FALSE, message=FALSE}
quantmod::getSymbols("AAPL")
```
```{r}
head(AAPL)
```
You can see how RCoinAPI mimics the column naming conventions and XTS object structure of your existing [quantmod](https://cran.r-project.org/web/packages/quantmod/quantmod.pdf) - [quantstrat](https://github.com/braverock/quantstrat) workflow. Obviously, unlike stocks, there is no 'adjusted' column in crypto data.

Now this is not going to be a tutorial on backtesting trading strategies with [quantstrat - click here for the details](https://github.com/braverock/quantstrat).

We're just going to quickly set up a backtest to see how nicely RCoinAPI plays with your existing Quantstrat workflow with a couple of big codeblocks that do all the things referenced in the link above:

### Step 2: Setup portfolio, account, Golden/Death cross strategy for Quantstrat

This is taken directly from the [Quantstrat](https://github.com/braverock/quantstrat) README, with the stock symbol replaced by our crypto symbol:

```{r, warning=FALSE, message=FALSE}
library(quantstrat)
```

```{r}
# Specify the symbol, currency and stock metadata

stock.str='ETH_USD' # what are we trying it on
currency('USD')
stock(stock.str,currency='USD',multiplier=1)

# Set up the portfolio, account and variables for date, balance, etc

startDate="2016-01-01"
initEq=1000000
portfolio.st='macross'
account.st='macross'

#Intitialize

initPortf(portfolio.st,symbols=stock.str)
initAcct(account.st,portfolios=portfolio.st, initEq=initEq)
initOrders(portfolio=portfolio.st)
stratMACROSS<- strategy(portfolio.st)
```
### Step 3: Create the Golden/Death cross strategy and add it to our portfolio

```{r}
stratMACROSS <- add.indicator(strategy = stratMACROSS, name = "SMA", arguments = list(x=quote(Cl(mktdata)[,1]), n=50),label= "ma50" )
stratMACROSS <- add.indicator(strategy = stratMACROSS, name = "SMA", arguments = list(x=quote(Cl(mktdata)[,1]), n=200),label= "ma200")

stratMACROSS <- add.signal(strategy = stratMACROSS,name="sigCrossover",arguments = list(columns=c("ma50","ma200"), relationship="gte"),label="ma50.gt.ma200")
stratMACROSS <- add.signal(strategy = stratMACROSS,name="sigCrossover",arguments = list(column=c("ma50","ma200"),relationship="lt"),label="ma50.lt.ma200")

stratMACROSS <- add.rule(strategy = stratMACROSS,name='ruleSignal', arguments = list(sigcol="ma50.gt.ma200",sigval=TRUE, orderqty=100, ordertype='market', orderside='long'),type='enter')
stratMACROSS <- add.rule(strategy = stratMACROSS,name='ruleSignal', arguments = list(sigcol="ma50.lt.ma200",sigval=TRUE, orderqty='all', ordertype='market', orderside='long'),type='exit')
```

### Step 4: Apply strategy, update portfolio and view results!

```{r}
# Apply Strategy

out<-applyStrategy(strategy=stratMACROSS , portfolios=portfolio.st)

# Update portfolio

updatePortf(Portfolio='macross',Dates=paste('::',as.Date(Sys.time()),sep=''))

# Chart portfolio returns

chart.Posn(Portfolio='macross',Symbol=stock.str, TA=c("add_SMA(n=50,col='red')","add_SMA(n=200,col='blue')"))
```

### Conclusion

RCoinAPI lets you use the fabulous CoinAPI.io REST API to easily develop and backtest crypto strategies on your existing pipeline with little modification, if any.

This is of course a new package, so feedback/issues are most welcome!

https://github.com/Ramshreyas/rcoinapi
